
### Reading Data from CSV
```{r}
activity<-read.csv("activity.csv", header=T, sep=",")

```

### Creation of Histogram
```{r}
dailysteps<-aggregate(activity$steps, by=list(Day=activity$date), FUN=sum)
print(dailysteps)
hist(dailysteps$x, xlab="Steps", main="Total Steps per Day")

```

### Calculation Mean and Median
```{r}
Avgsteps <- as.integer(mean(dailysteps$x,na.rm=T))
paste("The average number of steps taken each day:", Avgsteps)
Quartile2<- median(dailysteps$x,na.rm=T)
paste("The Median number of steps taken each day:", Quartile2)
```

### Time Series on Average

```{r}
Avgtimeseries<- aggregate(activity$steps, by=list(Interval=activity$interval), FUN=mean, na.rm=T)
Defineddata <- Avgtimeseries[!is.na(Avgtimeseries$x),]
library(ggplot2)
ggplot(Defineddata,aes(Interval,x))+geom_line()+geom_point()+ylab("Number of steps")+ggtitle("Average steps per interval")
```

### 5-minute interval, on average,that contains the maximum number of steps

```{r}
Maxvalue <- as.integer(max(Defineddata$x,na.rm=T))
Interval<-Defineddata$Interval[as.integer(Defineddata$x)==Maxvalue]
paste("The interval for max steps is ",Interval,sep="")
```
### Count of Missing Values
```{r}
paste("The total Missing Values are:",sum(is.na(activity$steps)))
```
### Imputing Missing Values by replacing with Median values of day & interval data

```{r}
Modifieddata <- activity
Nas<- is.na(Modifieddata$steps)
Medianinterval<- tapply(Modifieddata$steps, Modifieddata$interval, median, na.rm=TRUE, simplify = TRUE)
Modifieddata$steps[Nas] <- Medianinterval[as.character(Modifieddata$interval[Nas])]
```

### Using Imputed Missing Values, creating Histogram

```{r}
Moddatasteps<-aggregate(Modifieddata$steps, by=list(Date=Modifieddata$date), FUN=sum)
print(Moddatasteps)
hist(Moddatasteps$x, col="Red", xlab="Steps" , main="#Steps taken per day")
hist(dailysteps$x, col="blue", xlab="Steps", main="#Steps taken per day", add=T)
legend("topright", c("NA Data", "Non-NA Data"), fill=c("Red", "blue") )
```

### Mean of Imputed Missing Values
``` {r}
ModdataMean<-as.integer(mean(Moddatasteps$x))
paste("The average number of steps taken each day:", ModdataMean)
```
### Median of Imputed Missing Values

``` {r}
ModdataMedian<- median(Moddatasteps$x)
paste("The Median number of steps taken each day:", ModdataMedian)
```

### Activity patterns between Weekdays and Weekends

``` {r}
Modifieddata$Wday<-ifelse(weekdays(as.Date(Modifieddata$date,'%Y-%m-%d'))=="Saturday" | weekdays(as.Date(Modifieddata$date,'%Y-%m-%d'))=="Sunday","Weekend","Weekday")
Modifieddata$date<-strptime(Modifieddata$date,'%Y-%m-%d')
Modifieddata$wday<-factor(Modifieddata$Wday)
Moddatasteps1<-aggregate(Modifieddata$steps, by=list(wday=Modifieddata$wday, Interval = Modifieddata$interval), FUN=mean)
par(mfrow=c(2,1), mar = c(2,4,2,2))

plot(Moddatasteps1$Interval[Moddatasteps1$wday=="Weekday"],Moddatasteps1$x[Moddatasteps1$wday=="Weekday"], xlab="Interval", ylab="Steps per Interval", main="Weekday Interval by Steps",type="l",col="green")
plot(Moddatasteps1$Interval[Moddatasteps1$wday=="Weekend"],Moddatasteps1$x[Moddatasteps1$wday=="Weekend"], xlab="Interval", ylab="Steps per Interval", main="Weekend Interval by Steps",type="l",col="red")
```






